\documentclass[aps,prd,onecolumn,notitlepage,nofootinbib,superscriptaddress,11pt,floatfix]{revtex4-2}

% -------- packages --------
\usepackage{amsmath,amssymb,mathtools,bm}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xurl}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{hidelinks}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

% -------- macros --------
\newcommand{\dd}{\mathrm{d}}
\newcommand{\ee}{\mathrm{e}}
\newcommand{\ii}{\mathrm{i}}
\newcommand{\Tr}{\operatorname{Tr}}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\Span}{\operatorname{span}}
\newcommand{\Ker}{\operatorname{Ker}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cH}{\mathcal H}
\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}
\newcommand{\cM}{\mathcal M}
\newcommand{\cO}{\mathcal O}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\CP}{\mathbb{CP}}
\newcommand{\scrD}{\mathscr D}
\newcommand{\Order}{\mathcal O}
\setlength{\emergencystretch}{2em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

\title{\Large \bf \texorpdfstring{A Spin\(^c\) Projection-Dolbeault Derivation of Three Standard Model Generations in PSLT}{A Spinc Projection-Dolbeault Derivation of Three Standard Model Generations in PSLT}}

\author{Bo-Yu Chen}
\affiliation{Independent Researcher}

\date{May 1, 2026}

\begin{abstract}
We formulate the Projection Spectral Layer Theory (PSLT) as a first-principles projection-spectral derivation of the three-generation multiplicity of the Standard Model chiral family representation, conditional on the PSLT two-center projection data.
The compact projection surface is \(C=\CP^1\), the two projection branch points define the divisor \(R=p_+ + p_-\), and the generation line bundle is \(L_R=\cO(R)\simeq\cO(2)\).
The internal fermion operator is specified to be the Spin\(^c\) Dolbeault--Dirac operator
\[
\scrD_R=\sqrt2\left(\bar\partial_{L_R}+\bar\partial_{L_R}^\dagger\right)
\]
acting on \(\Lambda^{0,*}T^*C\otimes L_R\).
Hodge theory gives
\[
\Ker \scrD_R^+\cong H^0(C,L_R),
\qquad
\Ker \scrD_R^-\cong H^1(C,L_R).
\]
For \(C=\CP^1\) and \(L_R=\cO(2)\), Riemann--Roch and Serre duality give
\[
h^0(\CP^1,\cO(2))=3,
\qquad
h^1(\CP^1,\cO(2))=0.
\]
Provided the SM-charged chiral carrier is exactly this Spin\(^c\) generation sector and all other SM-charged internal sectors are absent from the kernel or fully paired and gapped, the low-energy four-dimensional chiral spectrum contains exactly three Standard Model families and no unpaired light SM-charged exotics.
The same two-center geometry supplies the conformal factor \(\Omega\) from a variational Poisson constraint, the scalar spectral operator \([-\nabla^2+V_{\rm eff}]\psi_n=\omega_n^2\psi_n\), and the scalar spectral data used in an effective formation/visibility probability law
\[
P_N(t)=
\frac{B_Ng_N^{\rm chiral}(1-\ee^{-\Gamma_N^{\rm eff}t})}
{\sum_{K=1}^{3}B_Kg_K^{\rm chiral}(1-\ee^{-\Gamma_K^{\rm eff}t})}.
\]
The scalarization weights \(\mu_{nN}\) select a hard-locked mode only when the locking gap exists, in which case \(\psi_N^{\rm lock}:=\psi_{n(N;D)}\), \(\omega_N:=\omega_{n(N;D)}\), and \(\Gamma_N^{\rm eff}=\Gamma_N\); otherwise \(\Gamma_N^{\rm eff}=\Gamma_N^{\rm soft}\).
Thus the generation count is a Spin\(^c\) index-theoretic consequence of the two-center projection divisor, while \((g_N^{\rm chiral},\Gamma_N^{\rm eff},B_N)\) describe degeneracy, kinetics, and visible-sector overlap of the three protected modes.
\end{abstract}

\maketitle
\tableofcontents
\newpage

% ============================================================
\section{Core Structure}
\label{sec:core_structure}

The construction has three logically distinct layers:
\begin{enumerate}
\item the \emph{SM charge layer}, where one minimal Standard Model family is fixed by gauge invariance, Yukawa invariance, and anomaly cancellation;
\item the \emph{internal fermion layer}, where the Spin\(^c\) Dolbeault--Dirac operator on the projection surface supplies the chiral zero-mode multiplicity;
\item the \emph{formation and visibility layer}, where the two-center conformal geometry supplies scalar spectral data for effective rates and visible-sector overlaps.
\end{enumerate}
The data needed for the Spin\(^c\) generation-multiplicity theorem are only
\begin{equation}
\boxed{
\mathfrak D_{\rm gen}
=
(C,R,L_R,\scrD_R).
}
\label{eq:generation_theorem_data}
\end{equation}
They fix \(\Ker\scrD_R^+\), hence the number of protected chiral generations.
The effective formation/visibility layer uses additional interface data
\begin{equation}
\boxed{
\mathfrak D_{\rm int}(D)
=
\left(
\pi_D,\mathfrak j_D,w_D,\mathcal J_{\rm vis}
\right).
}
\label{eq:interface_data}
\end{equation}
These interface data assign scalar profiles, rates, and visible overlaps to the protected modes; they are not inputs to the index-theoretic statement \(N_{\rm gen}=3\).
The core Hilbert-space statement is
\begin{equation}
\boxed{
\cH_{\rm chiral}^{\rm 4D}
=
\cR_{\rm SM}
\otimes
\Ker\scrD_R^+
=
\cR_{\rm SM}
\otimes
H^0(\CP^1,\cO(p_+ + p_-)).
}
\label{eq:core_hilbert}
\end{equation}
Since \(p_+ + p_-\) has degree two,
\begin{equation}
\cO(p_+ + p_-)\simeq \cO(2),
\qquad
\dim H^0(\CP^1,\cO(2))=3.
\label{eq:core_dimension}
\end{equation}
The low-energy chiral spectrum is therefore
\begin{equation}
\boxed{
\cH_{\rm chiral}^{\rm 4D}
=
\cR_{\rm SM}^{(1)}
\oplus
\cR_{\rm SM}^{(2)}
\oplus
\cR_{\rm SM}^{(3)}.
}
\label{eq:three_families}
\end{equation}
The family count is the dimension of the positive internal Spin\(^c\) fermion zero-mode space.

\subsection{Notation conventions}
\label{sec:notation_conventions}

Throughout the paper, \(D\) denotes the two-center separation parameter.
Dirac-type operators are written with script letters, such as \(\scrD_R\), \(\scrD_X\), \(\scrD_{\rm vec}\), and \(\scrD_{M_4}^{\rm SM}\).
The Bergman projector onto \(H^0(C,L_R)\) is \(P_R\), the collective-coordinate projector is \(P_N^{\rm cc}\), the one-dimensional Toeplitz-mode projector is \(\Pi_N=|u_N\rangle\langle u_N|\), and the observed layer probability is \(P_N(t;D,\eta)\).
The protected zero-mode degeneracy is denoted \(g_N^{\rm chiral}\); any unadorned degeneracy symbol is avoided in the chiral family count.

% ============================================================
\section{Parent Projection Data}
\label{sec:parent_data}

Let \(M_4\) be four-dimensional spacetime and let the compact projection surface be
\begin{equation}
C\simeq\CP^1.
\end{equation}
The two projection branch points define the divisor
\begin{equation}
R=p_+ + p_-,
\qquad
L_R=\cO(R)\simeq\cO(2).
\label{eq:LR_def}
\end{equation}
The parent action is organized as
\begin{equation}
S_{\rm FP}
=
S_{\rm grav}
+S_{\rm gauge}
+S_{\rm Higgs}
+S_{\rm fermion}
+S_\Omega^{\rm cov}
+S_{\rm proj}
+S_{\rm vis}.
\label{eq:parent_action}
\end{equation}
The projection sector fixes the topological class of \(L_R\), not a pointwise equality between a smooth curvature form and a delta-current.
The robust condition is the cohomological constraint
\begin{equation}
\boxed{
\left[\frac{\ii}{2\pi}F_{A_R}\right]
=
\operatorname{PD}(R)
=
[p_+]+[p_-]
\in H^2(C,\mathbb Z),
\qquad
R=p_+ + p_-.
}
\label{eq:Sproj_cohomology}
\end{equation}
Equivalently,
\begin{equation}
c_1(L_R)=\operatorname{PD}(R),
\qquad
\deg L_R=2.
\label{eq:degree_LR}
\end{equation}
When an action-like expression is useful, it should be read as a topological constraint or as a regulated current limit:
\begin{equation}
S_{\rm proj}^{\rm top}
=
\int_C\lambda_R
\left[
\frac{\ii}{2\pi}F_{A_R}
-J_R^{(\varepsilon)}
\right],
\label{eq:Sproj}
\end{equation}
where \(J_R^{(\varepsilon)}\) is any smooth representative of \(\operatorname{PD}(R)\) that tends, as a current, to \(\delta_{p_+}^{(2)}+\delta_{p_-}^{(2)}\).
The first-principles input is Eq.~\eqref{eq:Sproj_cohomology}; Eq.~\eqref{eq:Sproj} is only a regulated implementation of the same topological class.

\subsection{SM-charged fermion sector}
\label{sec:sm_fermion_sector}

The SM-charged internal fermion carrier is assumed to be exactly
\begin{equation}
\cE_{\rm gen}
=
\cR_{\rm SM}\otimes \cS_C,
\qquad
\cS_C=\Lambda^{0,*}T^*C\otimes L_R.
\label{eq:generation_carrier}
\end{equation}

Let
\begin{equation}
X=M_4\times C.
\end{equation}
The generation-sector product Dirac operator is
\begin{equation}
\boxed{
\scrD_X
=
\scrD_{M_4}^{\rm SM}\otimes 1
+
\gamma_5\otimes\scrD_R,
\qquad
\Gamma_X=\gamma_5\otimes\Gamma_C.
}
\label{eq:product_dirac}
\end{equation}
Here \(\scrD_{M_4}^{\rm SM}\) includes the four-dimensional SM gauge connection on \(\cR_{\rm SM}\), \(\Gamma_C\) is the internal Spin\(^c\) chirality, and \(\Gamma_X\) is the product chirality.
The generation-sector fermion action is
\begin{equation}
\boxed{
S_{\rm fermion}^{\rm gen}
=
\int_{M_4\times C}
\dd{\rm vol}_{M_4}\,\dd{\rm vol}_{C}\,
\overline{\Psi}\,\ii\scrD_X\Psi .
}
\label{eq:product_fermion_action}
\end{equation}
The internal mode expansion is
\begin{equation}
\Psi(x,y)
=
\sum_{\alpha}\psi_\alpha^+(x)u_\alpha^+(y)
+
\sum_{\beta}\psi_\beta^-(x)u_\beta^-(y)
+
\sum_{\lambda>0}\Psi_\lambda(x)\chi_\lambda(y),
\label{eq:product_mode_expansion}
\end{equation}
where
\begin{equation}
\scrD_Ru_\alpha^+=0,
\qquad
u_\alpha^+\in\Ker\scrD_R^+,
\qquad
\scrD_Ru_\beta^-=0,
\qquad
u_\beta^-\in\Ker\scrD_R^-.
\label{eq:internal_zero_mode_conditions}
\end{equation}
After a fixed product-chirality projection, internal positive and negative zero modes produce opposite four-dimensional Weyl chiralities.
We choose the product chirality so that \(\Ker\scrD_R^+\) carries the left-handed SM family representation \(\cR_{\rm SM}\); \(\Ker\scrD_R^-\) would supply the opposite four-dimensional chirality in the same generation sector.
Thus the chain is explicit:
\begin{equation}
\text{internal Spin}^c\text{ zero mode}
\quad\Longrightarrow\quad
\text{massless 4D Weyl fermion}
\quad\Longrightarrow\quad
\text{SM chiral generation}.
\end{equation}

All other SM-charged internal sectors are required to be vectorlike and genuinely gapped:
\begin{equation}
\cE_{\rm fermion}^{\rm SM}
=
\cE_{\rm gen}
\oplus
\cE_{\rm vec}.
\label{eq:exclusivity_vec}
\end{equation}
The condition is stronger than \(\operatorname{ind}\scrD_{\rm vec}=0\).
It requires either
\begin{equation}
\Ker\scrD_{\rm vec}=0,
\label{eq:vec_no_kernel}
\end{equation}
or
\begin{equation}
\begin{aligned}
\dim\Ker\scrD_{\rm vec}^+
\;&=
\dim\Ker\scrD_{\rm vec}^-,
\\
M_{\rm vec}:\Ker\scrD_{\rm vec}^+
\;&\longrightarrow
\Ker\scrD_{\rm vec}^-,
\qquad
M_{\rm vec}\text{ is full rank and gauge invariant}.
\end{aligned}
\label{eq:vectorlike_gap_condition}
\end{equation}
Index zero only excludes extra net chirality.
Equation~\eqref{eq:vec_no_kernel} or Eq.~\eqref{eq:vectorlike_gap_condition} is the additional low-energy condition that excludes unpaired massless SM-charged vectorlike exotics.
SM-neutral sectors may be present, but they do not carry generation quantum numbers:
\begin{equation}
\cE_{\rm fermion}
=
\cE_{\rm gen}
\oplus
\cE_{\rm vec}
\oplus
\cE_{\rm neutral}.
\label{eq:fermion_sector_decomp}
\end{equation}
This is the exclusivity condition needed for an exact no-fourth-generation theorem.
Without it, an additional SM-charged internal bundle with nonzero index could produce extra chiral matter.

% ============================================================
\section{One Standard Model Family}
\label{sec:one_family}

The local anomaly equations use the Standard Model Lie algebra.
When a global group and charge lattice are needed, we take
\begin{equation}
G_{\rm SM}
=
\frac{SU(3)_c\times SU(2)_L\times U(1)_Y}{\mathbb Z_6}.
\label{eq:gsm_global}
\end{equation}
This global choice fixes the conventional hypercharge unit used below; without it, the local equations determine hypercharge only up to an overall \(U(1)_Y\) normalization.
For one left-handed Weyl family, take
\begin{equation}
Q:(3,2)_{Y_Q},\quad
u^c:(\bar3,1)_{Y_u},\quad
d^c:(\bar3,1)_{Y_d},
\qquad
L:(1,2)_{Y_L},\quad
e^c:(1,1)_{Y_e},
\end{equation}
with Higgs
\begin{equation}
H:(1,2)_h.
\end{equation}
Set \(Y_Q=q\).
Gauge invariance of the Yukawa couplings gives
\begin{align}
QHu^c:&\qquad q+h+Y_u=0,
&
QH^\dagger d^c:&\qquad q-h+Y_d=0,
\\
LH^\dagger e^c:&\qquad Y_L-h+Y_e=0.
\end{align}
Hence
\begin{equation}
Y_u=-q-h,\qquad
Y_d=-q+h,\qquad
Y_e=h-Y_L.
\label{eq:yukawa_hypercharge_constraints}
\end{equation}
The \(SU(3)^2U(1)\) anomaly gives
\begin{equation}
2Y_Q+Y_u+Y_d=0,
\end{equation}
which is automatic after Eq.~\eqref{eq:yukawa_hypercharge_constraints}.
The pure color anomaly also cancels:
\begin{equation}
\mathcal A_{SU(3)^3}
=
2A(3)+A(\bar3)+A(\bar3)
=
2A(3)-A(3)-A(3)
=0,
\label{eq:su3_cubic_anomaly}
\end{equation}
where the factor of two comes from the two \(SU(2)_L\) components of \(Q\), and \(A(\bar3)=-A(3)\).
The \(SU(2)^2U(1)\) anomaly gives
\begin{equation}
3Y_Q+Y_L=0,
\qquad
Y_L=-3q.
\label{eq:su2_anomaly}
\end{equation}
The mixed gravitational anomaly requires
\begin{equation}
6Y_Q+3Y_u+3Y_d+2Y_L+Y_e=0.
\label{eq:grav_anomaly}
\end{equation}
Substitution gives
\begin{equation}
6q+3(-q-h)+3(-q+h)+2(-3q)+(h+3q)=0,
\end{equation}
so
\begin{equation}
h=3q.
\end{equation}
Therefore
\begin{equation}
Y_u=-4q,\qquad
Y_d=2q,\qquad
Y_L=-3q,\qquad
Y_e=6q,\qquad
Y_H=3q.
\end{equation}
The \(U(1)^3\) anomaly cancels:
\begin{equation}
6q^3+3(-4q)^3+3(2q)^3+2(-3q)^3+(6q)^3
=0.
\end{equation}
There is no Witten global \(SU(2)\) anomaly.
One family contains
\begin{equation}
3\text{ color copies of }Q
+
1\text{ lepton doublet}
=4
\label{eq:witten_su2_count}
\end{equation}
left-handed \(SU(2)_L\) Weyl doublets, which is even.
For three families the number is \(12\), still even.
With \(q=1/6\),
\begin{equation}
\boxed{
(Y_Q,Y_u,Y_d,Y_L,Y_e,Y_H)
=
\left(
\frac16,
-\frac23,
\frac13,
-\frac12,
1,
\frac12
\right).
}
\label{eq:SM_hypercharges}
\end{equation}
A sterile \(\nu^c:(1,1)_0\) may be added without changing these anomaly equations.

\begin{proposition}
Within the minimal one-family chiral field content above, and assuming the Yukawa couplings \(QHu^c\), \(QH^\dagger d^c\), and \(LH^\dagger e^c\), the local anomaly equations fix the hypercharge pattern up to the overall normalization of \(U(1)_Y\).
The choice in Eq.~\eqref{eq:gsm_global} fixes the conventional unit \(q=1/6\).
\end{proposition}

% ============================================================
\section{\texorpdfstring{Spin\(^c\) Dolbeault--Dirac Zero Modes}{Spinc Dolbeault-Dirac Zero Modes}}
\label{sec:spinc_dirac}

The internal fermion operator is not the ordinary spin Dirac operator.
It is the Spin\(^c\) Dolbeault--Dirac operator
\begin{equation}
\boxed{
\scrD_R
=
\sqrt2
\left(
\bar\partial_{L_R}
+\bar\partial_{L_R}^\dagger
\right)
}
\label{eq:Dolbeault_Dirac}
\end{equation}
acting on
\begin{equation}
\cS_C
=
\Lambda^{0,*}T^*C\otimes L_R.
\label{eq:spinc_spinor_bundle}
\end{equation}
We use the canonical Spin\(^c\) structure on the complex curve \(C\), whose untwisted spinor bundle is \(\Lambda^{0,*}T^*C\).
The line bundle \(L_R\) is an auxiliary twisting bundle for the Dolbeault--Dirac operator, not the Spin\(^c\) determinant line itself.
The relevant index is therefore the Dolbeault index
\begin{equation}
\operatorname{ind}\scrD_R
=
\chi(C,L_R)
=
h^0(C,L_R)-h^1(C,L_R).
\label{eq:dolbeault_index}
\end{equation}
Its internal chirality decomposition is
\begin{equation}
\cS_C^+
=
\Lambda^{0,0}T^*C\otimes L_R,
\qquad
\cS_C^-
=
\Lambda^{0,1}T^*C\otimes L_R.
\label{eq:chirality_decomp}
\end{equation}
By Hodge theory,
\begin{equation}
\boxed{
\Ker\scrD_R^+
\cong
H^0(C,L_R),
\qquad
\Ker\scrD_R^-
\cong
H^1(C,L_R).
}
\label{eq:hodge_kernel}
\end{equation}
This is the step that converts a holomorphic-section count into an internal fermion zero-mode theorem.

\begin{remark}
The Spin\(^c\) choice is essential for the stated bundle \(L_R=\cO(2)\).
For an ordinary spin Dirac operator on \(\CP^1\), the spin bundle contributes \(K_C^{1/2}=\cO(-1)\).
Twisting an ordinary spin Dirac operator only by \(\cO(2)\) would count
\[
H^0(\CP^1,K_C^{1/2}\otimes\cO(2))
=
H^0(\CP^1,\cO(1)),
\]
which is two-dimensional.
Equivalently, an ordinary spin-Dirac presentation would need the twist
\[
E=K_C^{-1/2}\otimes L_R=\cO(1)\otimes\cO(2)=\cO(3)
\]
so that \(K_C^{1/2}\otimes E=L_R\).
\end{remark}

% ============================================================
\section{Three-Generation Theorem}
\label{sec:three_generation_theorem}

\begin{theorem}[PSLT Spin\(^c\) three-generation theorem]
\label{thm:three_gen}
Let \(C=\CP^1\), \(R=p_+ + p_-\), and \(L_R=\cO(R)\simeq\cO(2)\).
Let the SM-charged generation carrier be
\[
\cR_{\rm SM}\otimes(\Lambda^{0,*}T^*C\otimes L_R),
\]
with internal operator \(\scrD_R\) as in Eq.~\eqref{eq:Dolbeault_Dirac}.
Assume the product Dirac action is Eq.~\eqref{eq:product_fermion_action}, the product chirality is Eq.~\eqref{eq:product_dirac}, every other SM-charged internal sector satisfies the full vectorlike gap condition of Eq.~\eqref{eq:vec_no_kernel} or Eq.~\eqref{eq:vectorlike_gap_condition}, and all remaining chiral sectors are SM-neutral.
Then the low-energy four-dimensional chiral SM spectrum contains exactly three generations:
\begin{equation}
N_{\rm gen}
=
\dim\Ker\scrD_R^+
-\dim\Ker\scrD_R^-
=3.
\label{eq:Ngen_index}
\end{equation}
Moreover, since \(\Ker\scrD_R^-=0\), the positive internal zero-mode space itself is three-dimensional.
\end{theorem}

\begin{proof}
Riemann--Roch for a line bundle \(L\) on a compact Riemann surface gives
\begin{equation}
h^0(C,L)-h^1(C,L)=\deg L+1-g(C).
\end{equation}
For \(C=\CP^1\), \(g(C)=0\).
Because \(R=p_+ + p_-\), \(\deg L_R=2\).
Therefore
\begin{equation}
h^0(C,L_R)-h^1(C,L_R)=3.
\label{eq:rr_index}
\end{equation}
Serre duality gives
\begin{equation}
h^1(C,L_R)
=
h^0(C,K_C\otimes L_R^{-1}).
\end{equation}
On \(\CP^1\),
\begin{equation}
K_C=\cO(-2),
\qquad
L_R^{-1}=\cO(-2),
\end{equation}
so
\begin{equation}
K_C\otimes L_R^{-1}=\cO(-4).
\end{equation}
A negative-degree line bundle on \(\CP^1\) has no nonzero holomorphic sections.
Thus
\begin{equation}
h^1(C,L_R)=0,
\qquad
h^0(C,L_R)=3.
\end{equation}
Using Eq.~\eqref{eq:hodge_kernel},
\begin{equation}
\dim\Ker\scrD_R^+=3,
\qquad
\dim\Ker\scrD_R^-=0.
\end{equation}
The product Dirac reduction in Eqs.~\eqref{eq:product_dirac}--\eqref{eq:internal_zero_mode_conditions} turns these internal zero modes into massless four-dimensional Weyl fermions.
The vectorlike gap condition prevents additional SM-charged chiral generations and also removes unpaired massless SM-charged vectorlike exotics.
\end{proof}

In an affine coordinate \(\zeta\) on \(\CP^1\),
\begin{equation}
H^0(\CP^1,\cO(2))
=
\Span\{1,\zeta,\zeta^2\}.
\label{eq:holomorphic_basis}
\end{equation}
This span is only a vector space until a physical basis is chosen.
The family count is basis-independent; the labels \(N=1,2,3\) require a canonical Hermitian operator.

% ============================================================
\section{Canonical Generation Basis}
\label{sec:canonical_basis}

The two branch points alone determine the divisor and the family count, but a physical basis also needs the normalization of the affine coordinate on \(C\).
Placing \(p_+\) at \(0\) and \(p_-\) at \(\infty\) leaves the residual freedom \(\zeta_R\mapsto a\zeta_R\).
In PSLT this freedom is fixed by the two-center projection map from the spatial chart to the compact projection surface.

\subsection{Projection map and coordinate normalization}
\label{sec:projection_map}

Let \((\rho,z_{\rm ax},\varphi)\) be cylindrical coordinates on \(\mathbb R^3\), with the ordered centers
\begin{equation}
x_\pm:\quad \rho=0,\qquad z_{\rm ax}=\pm D/2.
\label{eq:spatial_centers}
\end{equation}
With regulator \(\varepsilon>0\), define
\begin{equation}
r_\pm
=
\sqrt{\rho^2+(z_{\rm ax}\mp D/2)^2+\varepsilon^2}.
\label{eq:rpm_projection}
\end{equation}
The physical affine coordinate is
\begin{equation}
\boxed{
\zeta_R(\rho,z_{\rm ax},\varphi;D,\varepsilon)
=
\left(\frac{r_+}{r_-}\right)^{1/2}\ee^{\ii\varphi}.
}
\label{eq:zeta_projection}
\end{equation}
The projection map is
\begin{equation}
\boxed{
\pi_D:\mathbb R^3\longrightarrow C\simeq\CP^1,
\qquad
\pi_D(\rho,z_{\rm ax},\varphi)
=
[1:\zeta_R(\rho,z_{\rm ax},\varphi;D,\varepsilon)].
}
\label{eq:piD_def}
\end{equation}
In the collapsed-core limit \(\varepsilon\to0\),
\begin{equation}
\pi_D(x_+)=p_+=[1:0],
\qquad
\pi_D(x_-)=p_-=[0:1].
\label{eq:piD_centers}
\end{equation}
For finite \(\varepsilon\), the source cores are mapped to regulated neighborhoods of the branch points.
The normalization is fixed by the midplane condition
\begin{equation}
z_{\rm ax}=0
\quad\Longrightarrow\quad
|\zeta_R|=1,
\label{eq:zeta_midplane}
\end{equation}
and the residual \(U(1)\) phase is fixed by the origin of the axial angle \(\varphi\).
Thus the earlier scale freedom \(\zeta_R\mapsto a\zeta_R\) is removed by the physical projection geometry rather than by an arbitrary Gram--Schmidt convention.

\subsection{Toeplitz basis}
\label{sec:toeplitz_basis}

Let \(P_R\) be the Bergman projector from \(L^2(C,L_R)\) onto \(H^0(C,L_R)\), using the Fubini--Study metric on \(C=\CP^1\) and the induced Hermitian metric on \(L_R\).
Using the coordinate \(\zeta_R\) fixed by Eq.~\eqref{eq:zeta_projection}, the associated axial moment-map function is
\begin{equation}
\mu_R(\zeta_R,\bar\zeta_R)
=
\frac{|\zeta_R|^2-1}{|\zeta_R|^2+1}.
\label{eq:moment_map}
\end{equation}
Define the finite-dimensional Toeplitz operator
\begin{equation}
\boxed{
\mathcal T_R=P_RM_{\mu_R}P_R
}
\label{eq:Toeplitz}
\end{equation}
on \(H^0(C,L_R)\), where \(M_{\mu_R}\) denotes multiplication by \(\mu_R\).
The generation basis is defined by
\begin{equation}
\mathcal T_Ru_N=\tau_Nu_N,
\qquad
u_N\in H^0(C,L_R),
\qquad
N=1,2,3.
\label{eq:uN_basis}
\end{equation}
For the symmetric two-center placement and the standard Fubini--Study/Bergman inner product, this basis is equivalent, up to normalization and ordering, to the spin-one monomial basis
\begin{equation}
1,\qquad \zeta,\qquad \zeta^2.
\end{equation}
The Toeplitz definition is the physical statement; the monomial basis is only a convenient coordinate representation.

% ============================================================
\section{Two-Center Conformal Geometry}
\label{sec:two_center_geometry}

The two-center conformal factor is obtained in the static sector.
The covariant parent term \(S_\Omega^{\rm cov}\) in Eq.~\eqref{eq:parent_action} is not specified by the spatial expression below; rather, under the static two-center ansatz it reduces to the three-dimensional variational energy functional
\begin{equation}
E_\Omega
=
\frac{\kappa}{2}
\int_{\mathbb R^3}\dd^3x\,|\nabla\Omega|^2
-4\pi\kappa
\int_{\mathbb R^3}\dd^3x\,\sigma(x)(\Omega-1),
\label{eq:E_Omega}
\end{equation}
with
\begin{equation}
\sigma(x)
=
a\left[\rho_\varepsilon(x-x_+)+\rho_\varepsilon(x-x_-)\right].
\label{eq:sigma}
\end{equation}
Variation gives
\begin{equation}
\delta E_\Omega
=
-\kappa
\int_{\mathbb R^3}\dd^3x\,
\left(\nabla^2\Omega+4\pi\sigma\right)\delta\Omega,
\end{equation}
hence
\begin{equation}
\boxed{
\nabla^2\Omega=-4\pi\sigma.
}
\label{eq:Poisson}
\end{equation}
Let \((\rho,z_{\rm ax},\varphi)\) be cylindrical coordinates on \(\mathbb R^3\), with centers at
\begin{equation}
x_\pm:\quad \rho=0,\qquad z_{\rm ax}=\pm D/2.
\end{equation}
For
\begin{equation}
\rho_\varepsilon(r)
=
\frac{3\varepsilon^2}{4\pi(r^2+\varepsilon^2)^{5/2}},
\qquad
\int_{\mathbb R^3}\dd^3x\,\rho_\varepsilon=1,
\end{equation}
the asymptotically flat solution is
\begin{equation}
\boxed{
\Omega(\rho,z_{\rm ax};D)
=
1+a\left(\frac1{r_+}+\frac1{r_-}\right),
\qquad
r_\pm
=
\sqrt{\rho^2+(z_{\rm ax}\mp D/2)^2+\varepsilon^2}.
}
\label{eq:Omega_solution}
\end{equation}

% ============================================================
\section{Geometry-to-Spectrum Map}
\label{sec:geometry_spectrum}

We use the mostly-plus convention
\begin{equation}
\eta_{\mu\nu}=\diag(-,+,+,+),
\qquad
\Box_\eta=-\partial_t^2+\nabla^2,
\label{eq:signature}
\end{equation}
and the curvature convention
\begin{equation}
R^\rho{}_{\sigma\mu\nu}
=
\partial_\mu\Gamma^\rho_{\nu\sigma}
-\partial_\nu\Gamma^\rho_{\mu\sigma}
+\Gamma^\rho_{\mu\lambda}\Gamma^\lambda_{\nu\sigma}
-\Gamma^\rho_{\nu\lambda}\Gamma^\lambda_{\mu\sigma}.
\label{eq:curvature_convention}
\end{equation}
For the static conformally flat metric
\begin{equation}
g_{\mu\nu}=\Omega^2(x)\eta_{\mu\nu},
\end{equation}
this gives
\begin{equation}
R=-6\Omega^{-3}\nabla^2\Omega.
\label{eq:Ricci_scalar}
\end{equation}
Consider
\begin{equation}
(\Box_g-m_0^2-\xi R)\Phi=0,
\qquad
\Phi(t,x)=\ee^{-\ii\omega t}\Omega^{-1}(x)\psi(x).
\end{equation}
Using
\begin{equation}
\left(\Box_g-\frac16R\right)(\Omega^{-1}\psi)
=
\Omega^{-3}\Box_\eta\psi,
\end{equation}
one obtains
\begin{equation}
\left[
-\nabla^2
+m_0^2\Omega^2
+(1-6\xi)\Omega^{-1}\nabla^2\Omega
\right]\psi
=
\omega^2\psi.
\label{eq:scalar_operator_derived}
\end{equation}
Define
\begin{equation}
V_{\rm eff}
=
m_0^2\Omega^2
+(1-6\xi)\Omega^{-1}\nabla^2\Omega.
\label{eq:Veff}
\end{equation}
Then
\begin{equation}
\boxed{
[-\nabla^2+V_{\rm eff}]\psi_n=\omega_n^2\psi_n.
}
\label{eq:schrodinger}
\end{equation}
This scalar spectral problem governs formation barriers and visible overlap profiles.
It does not determine the number of chiral SM generations; that number is fixed by \(\scrD_R\).

% ============================================================
\section{Degeneracy, Kinetics, Visibility, and Formation}
\label{sec:probability_modules}

The structures in this section are an effective formation/visibility model built on the Spin\(^c\) generation theorem.
They use scalar spectral data and two-center collective coordinates to parametrize rates and overlaps; they do not supply an independent proof of the number of chiral SM generations.
The interface data used below are precisely \(\mathfrak D_{\rm int}(D)\) from Eq.~\eqref{eq:interface_data}; changing them changes the effective formation/visibility model, not the Spin\(^c\) multiplicity result.

For the protected chiral sector, let \(\Pi_N=|u_N\rangle\langle u_N|\) be the projector onto the Toeplitz eigenmode \(u_N\).
The chiral degeneracy is
\begin{equation}
g_N^{\rm chiral}
=
\Tr_{\cH_{\rm gen}}\Pi_N,
\qquad
\cH_{\rm gen}=H^0(\CP^1,\cO(2)).
\end{equation}
Thus
\begin{equation}
\boxed{
g_1^{\rm chiral}=g_2^{\rm chiral}=g_3^{\rm chiral}=1,
\qquad
g_{N\ge4}^{\rm chiral}=0.
}
\label{eq:gN}
\end{equation}

\subsection{Generation-to-spatial mode assignment}
\label{sec:mode_locking}

The protected generation basis \(u_N\in H^0(C,L_R)\) and the scalar spatial eigenmodes \(\psi_n\) of Eq.~\eqref{eq:schrodinger} are not the same objects.
The former are Spin\(^c\) zero modes on \(C\); the latter are eigenfunctions of a Schrödinger operator on the spatial two-center chart.
We reserve \(N=1,2,3\) for protected generation labels and \(n\) for scalar spectral labels.
Define
\begin{equation}
\cH_{\rm gen}
=
H^0(C,L_R),
\qquad
\cH_\Omega(D)
=
L^2(\mathbb R^3,\dd\mu_{\rm cyl}),
\qquad
\dd\mu_{\rm cyl}
=
\rho\,\dd\rho\,\dd z_{\rm ax}\,\dd\varphi,
\label{eq:gen_scalar_spaces}
\end{equation}
and
\begin{equation}
L_\Omega(D):=-\nabla^2+V_{\rm eff}(\cdot;D),
\qquad
L_\Omega(D)\psi_n(\cdot;D)
=
\omega_n^2(D)\psi_n(\cdot;D).
\label{eq:LOmega_modes}
\end{equation}
The projection map \(\pi_D\) pulls the generation bundle to the spatial chart:
\begin{equation}
\widehat L_R:=\pi_D^*L_R,
\qquad
\widehat h_R:=\pi_D^*h_R,
\qquad
\widehat u:=\pi_D^*u
\in
\Gamma(\mathbb R^3,\widehat L_R).
\label{eq:pullback_generation_bundle}
\end{equation}
To attach scalar barrier data to a protected generation, introduce the linear raw scalarization operator
\begin{equation}
\boxed{
\widetilde{\mathcal C}_D:\cH_{\rm gen}\longrightarrow \cH_\Omega(D),
\qquad
\widetilde{\mathcal C}_Du
=
w_D^{1/2}\,
\left\langle
\mathfrak j_D,
\pi_D^*u
\right\rangle_{\widehat h_R}.
}
\label{eq:scalarization_operator}
\end{equation}
Here \(\mathfrak j_D\in\Gamma(\mathbb R^3,\widehat L_R)\) is the locking/probe section supplied by the two-center projection data, and \(w_D\ge0\) is a scalar density weight.
With our convention that the Hermitian pairing is antilinear in the first entry and linear in the second, \(\widetilde{\mathcal C}_D\) is linear in \(u\).
The raw scalar profile is assumed nonzero on the protected modes \(u_N\).
The normalized profile map is the generally nonlinear map
\begin{equation}
\boxed{
c_D(u)
=
\frac{\widetilde{\mathcal C}_Du}
{\|\widetilde{\mathcal C}_Du\|_{\cH_\Omega(D)}}.
}
\label{eq:normalized_scalar_profile}
\end{equation}
The spectral weights of a generation mode against scalar eigenmodes are
\begin{equation}
\boxed{
\mu_{nN}(D)
=
\left|
\left\langle
\psi_n(\cdot;D),
c_D(u_N)
\right\rangle_{\cH_\Omega(D)}
\right|^2.
}
\label{eq:spectral_weights}
\end{equation}
For a normalized discrete scalar spectral resolution, \(\sum_n\mu_{nN}=1\).
If the scalar operator has a continuous component, Eq.~\eqref{eq:spectral_weights} is replaced by the projection-valued spectral measure
\begin{equation}
\dd\mu_N^D(\lambda)
=
\left\|
\dd E_\lambda(D)\,c_D(u_N)
\right\|_{\cH_\Omega(D)}^2.
\label{eq:spectral_measure}
\end{equation}
Only when a unique scalar mode dominates do we define a hard mode-locking map.
The condition is
\begin{equation}
n(N;D)
=
\operatorname*{arg\,max}_{n}\mu_{nN}(D),
\qquad
\mu_{n(N;D),N}(D)
-
\sup_{m\ne n(N;D)}\mu_{mN}(D)
\ge
\Delta_{\rm lock}>0.
\label{eq:locking_gap}
\end{equation}
In that regime,
\begin{equation}
\mathcal I_D(u_N):=\psi_{n(N;D)}(\cdot;D),
\qquad
\psi_N^{\rm lock}:=\psi_{n(N;D)},
\qquad
\omega_N(D):=\omega_{n(N;D)}(D).
\label{eq:hard_locking_map}
\end{equation}
If Eq.~\eqref{eq:locking_gap} fails, the generation must be assigned scalar data softly:
\begin{equation}
\Gamma_N^{\rm soft}(D,\eta)
=
\sum_n\mu_{nN}(D)\,\Gamma_n(D,\eta),
\label{eq:soft_rate_discrete}
\end{equation}
or, for a continuous spectral component,
\begin{equation}
\Gamma_N^{\rm soft}(D,\eta)
=
\int \Gamma(\lambda;D,\eta)\,\dd\mu_N^D(\lambda).
\label{eq:soft_rate_continuous}
\end{equation}
Here \(\Gamma_n\) is the scalar-mode formation rate for the \(n\)th eigenmode, computed by the same two-center Schur/WKB construction.
Thus the Spin\(^c\) theorem fixes \(u_N\), while \(\widetilde{\mathcal C}_D\), \(c_D\), \(\mu_{nN}\), and, only under Eq.~\eqref{eq:locking_gap}, \(\mathcal I_D\), supply the scalar formation interface.
All hard-locking quantities \(\omega_N\), \(\Gamma_N\), and \(|N,\pm\rangle\) below are understood only after Eq.~\eqref{eq:locking_gap}; otherwise \(\Gamma_N\) in the final probability law should be replaced by \(\Gamma_N^{\rm soft}\).

For kinetics in the hard-locking regime, the locked scalar mode \(\psi_N^{\rm lock}\) and the two centers define a collective-coordinate subspace
\begin{equation}
\cC_N=\Span\{|N,+\rangle,\ |N,-\rangle\}.
\end{equation}
Let \(P_N^{\rm cc}\) project onto \(\cC_N\), \(Q_N^{\rm cc}=1-P_N^{\rm cc}\), and let \(\cK_N(D,\eta)\) be the Euclidean fluctuation operator in this sector.
The dimensionless parameter \(\eta\) denotes the two-center overlap controlling kinetic mixing.
For the regulated source model, we take
\begin{equation}
\boxed{
\eta(D,\varepsilon)
=
\int_{\mathbb R^3}\dd^3x\,
\sqrt{
\rho_\varepsilon(x-x_+)\rho_\varepsilon(x-x_-)
},
\qquad
0\le \eta\le1.
}
\label{eq:eta_def}
\end{equation}
It enters the fluctuation operator, WKB prefactors, and center mixing coefficient:
\begin{equation}
\cK_N=\cK_N(D,\eta),
\qquad
A_{N,\pm}=A_{N,\pm}(D,\eta),
\qquad
\chi_N=\chi_N(D,\eta).
\label{eq:eta_dependencies}
\end{equation}
The Feshbach--Schur step assumes a gap on the eliminated complement:
\begin{equation}
0\notin
\operatorname{Spec}
\left(
Q_N^{\rm cc}\cK_N(D,\eta)Q_N^{\rm cc}
\right).
\label{eq:schur_gap_assumption}
\end{equation}
If this gap closes, the inverse below must be replaced by the corresponding reduced resolvent or pseudoinverse.
Under Eq.~\eqref{eq:schur_gap_assumption}, the Feshbach--Schur effective matrix is
\begin{equation}
\cM_N
=
P_N^{\rm cc}\cK_NP_N^{\rm cc}
-P_N^{\rm cc}\cK_NQ_N^{\rm cc}
(Q_N^{\rm cc}\cK_NQ_N^{\rm cc})^{-1}
Q_N^{\rm cc}\cK_NP_N^{\rm cc}.
\label{eq:Schur_matrix}
\end{equation}
In the two-center basis,
\begin{equation}
\cM_N
=
\begin{pmatrix}
\gamma_{N,+} &
\chi_N\sqrt{\gamma_{N,+}\gamma_{N,-}}\\
\chi_N\sqrt{\gamma_{N,+}\gamma_{N,-}}&
\gamma_{N,-}
\end{pmatrix},
\end{equation}
with WKB channel factors
\begin{equation}
\gamma_{N,\pm}
=
A_{N,\pm}\exp[-2S_{N,\pm}^{\rm WKB}],
\qquad
S_{N,\pm}^{\rm WKB}
=
\int_{\cB_{N,\pm}}\dd s\,
\sqrt{\left(V_{\rm eff}(s)-\omega_N^2\right)_+}.
\label{eq:WKB}
\end{equation}
Here
\begin{equation}
\cB_{N,\pm}
=
\{s\text{ on the } \pm\text{ channel}:\ V_{\rm eff}(s)>\omega_N^2\},
\label{eq:wkb_barrier_region}
\end{equation}
and \((x)_+=\max\{x,0\}\).
The formation rate is
\begin{equation}
\boxed{
\Gamma_N(D,\eta)
=
\max\{0,\lambda_+(\cM_N(D,\eta))\},
}
\label{eq:Gamma}
\end{equation}
where
\begin{equation}
\lambda_+(\cM_N)
=
\frac{\gamma_{N,+}+\gamma_{N,-}}{2}
+\frac12
\sqrt{
(\gamma_{N,+}-\gamma_{N,-})^2
+4\chi_N^2\gamma_{N,+}\gamma_{N,-}
}.
\end{equation}

For visibility, use the same pullback bundle from Eq.~\eqref{eq:pullback_generation_bundle}.
For the \(N\)th generation, the spatial representative is the section
\begin{equation}
\widehat u_N:=\pi_D^*u_N
\in
\Gamma(\mathbb R^3,\widehat L_R),
\label{eq:uN_pullback}
\end{equation}
not a scalar function.
The visible kernel is correspondingly a bundle-valued source
\begin{equation}
\mathcal J_{\rm vis}(D,\varepsilon)
\in
\Gamma(\mathbb R^3,\widehat L_R).
\label{eq:Jvis_bundle}
\end{equation}
The \(\varphi\)-dependence is therefore not discarded; in axially reduced formulas it has already been projected into the selected angular channel and absorbed into the chosen representative of \(\mathcal J_{\rm vis}\) and the measure factor.
The conformal Dirac and Higgs fields scale as
\begin{equation}
\Psi=\Omega^{-3/2}\psi,
\qquad
H=\Omega^{-1}\phi.
\end{equation}
Hence
\begin{equation}
\sqrt{-g}\,\bar\Psi H\Psi
\propto
\Omega^4\cdot\Omega^{-3/2}\cdot\Omega^{-1}\cdot\Omega^{-3/2}
=
\Omega^0.
\label{eq:weyl_yukawa}
\end{equation}
A mode-resolved Yukawa overlap is the Hermitian pairing on the pullback bundle:
\begin{equation}
\boxed{
y_N^{\rm eff}(D,\varepsilon)
=
y_0
\int_{\mathbb R^3}
\left\langle
\widehat u_N(x;D,\varepsilon),
\mathcal J_{\rm vis}(x;D,\varepsilon)
\right\rangle_{\widehat h_R}
\dd\mu_{\rm cyl}(x),
}
\label{eq:y_eff}
\end{equation}
We use the convention that the Hermitian pairing is antilinear in the first entry.
In a local frame \(\widehat e_R=\pi_D^*e_R\), write
\begin{equation}
\widehat u_N=U_N\widehat e_R,
\qquad
\mathcal J_{\rm vis}=J_{\rm vis}\widehat e_R,
\qquad
\widehat h_R(\widehat e_R,\widehat e_R)=H_R.
\label{eq:local_visibility_frame}
\end{equation}
Then
\begin{equation}
\left\langle
\widehat u_N,
\mathcal J_{\rm vis}
\right\rangle_{\widehat h_R}
=
H_R\,\overline{U_N}\,J_{\rm vis}.
\label{eq:local_visibility_pairing}
\end{equation}
This is independent of the frame.
Indeed, under \(\widehat e_R'=g\,\widehat e_R\), with \(g:\mathbb R^3\to\mathbb C^*\),
\begin{equation}
U_N'=g^{-1}U_N,
\qquad
J_{\rm vis}'=g^{-1}J_{\rm vis},
\qquad
H_R'=|g|^2H_R,
\end{equation}
and hence
\begin{equation}
H_R'\,\overline{U_N'}\,J_{\rm vis}'
=
H_R\,\overline{U_N}\,J_{\rm vis}.
\label{eq:frame_invariance}
\end{equation}
The earlier scalar-looking formula is only this local trivialized representative:
\begin{equation}
\begin{aligned}
y_N^{\rm eff}(D,\varepsilon)
=\;&
y_0
\int_0^\infty \rho\,\dd\rho
\int_{-\infty}^{\infty}\dd z_{\rm ax}
\int_0^{2\pi}\dd\varphi\,
\overline{U_N(\rho,z_{\rm ax},\varphi;D,\varepsilon)}
\\
&\times
f_L(\rho,z_{\rm ax})
f_R(\rho,z_{\rm ax})
W_{\rm frame}(\rho,z_{\rm ax},\varphi;D,\varepsilon).
\end{aligned}
\label{eq:y_eff_local}
\end{equation}
Here \(W_{\rm frame}\) is not an additional invariant object; it denotes the local representative of the bundle frame, Hermitian metric \(H_R\), visible source \(J_{\rm vis}\), angular-channel projection, Jacobian convention, and any remaining complex-conjugation convention.
When the visible kernel has already been reduced to an \(m=0\) axial channel, Eq.~\eqref{eq:y_eff_local} reduces to the earlier \(2\pi\rho\,\dd\rho\,\dd z_{\rm ax}\) form with the angular integral included in \(W_{\rm frame}\).
The normalized visible weight is
\begin{equation}
\boxed{
B_N
=
\frac{|y_N^{\rm eff}|^2}
{\sum_{I=1}^{3}|y_I^{\rm eff}|^2}.
}
\label{eq:BN}
\end{equation}
Equivalently,
\begin{equation}
B_N
=
\frac{\langle u_N|\mathcal O_{\rm vis}^\dagger\mathcal O_{\rm vis}|u_N\rangle}
{\sum_{I=1}^{3}
\langle u_I|\mathcal O_{\rm vis}^\dagger\mathcal O_{\rm vis}|u_I\rangle}.
\end{equation}

Finally, at the coarse-grained effective level, assume a single-rate Markovian formation law
\begin{equation}
\frac{\dd p_N}{\dd t}=\Gamma_N(1-p_N),
\qquad
p_N(0)=0
\end{equation}
has solution
\begin{equation}
p_N(t)=1-\ee^{-\Gamma_Nt}.
\end{equation}
Conditioning on the observation of one of the protected chiral layers gives
\begin{equation}
\boxed{
P_N(t;D,\eta)
=
\frac{
B_Ng_N^{\rm chiral}\left(1-\ee^{-\Gamma_N(D,\eta)t}\right)
}{
\sum_{K=1}^{3}
B_Kg_K^{\rm chiral}\left(1-\ee^{-\Gamma_K(D,\eta)t}\right)
}.
}
\label{eq:PN}
\end{equation}
Outside the hard-locking regime, the same conditional probability is used with \(\Gamma_N(D,\eta)\) replaced by \(\Gamma_N^{\rm soft}(D,\eta)\).

% ============================================================
\section{Conclusion}
\label{sec:conclusion}

The two-center PSLT projection data determine the divisor \(R=p_+ + p_-\) and the line bundle \(L_R=\cO(R)=\cO(2)\) on \(C=\CP^1\).
The SM-charged internal fermions are governed by the product Dirac action on \(M_4\times C\), with the internal Spin\(^c\) Dolbeault--Dirac operator acting on \(\Lambda^{0,*}T^*C\otimes L_R\).
The bundle \(L_R\) is the auxiliary Dolbeault twist, and the positive and negative internal zero modes are \(H^0(C,L_R)\) and \(H^1(C,L_R)\).
Riemann--Roch gives index three, and Serre duality gives \(H^1(C,L_R)=0\).
With all additional SM-charged sectors either absent from the kernel or fully paired by a gauge-invariant mass map, the theory therefore has exactly three low-energy chiral SM generations and no unpaired light SM-charged exotics.

After the raw scalarization operator \(\widetilde{\mathcal C}_D\), the normalized profile map \(c_D\), the spectral weights \(\mu_{nN}\), and, when the locking gap exists, the hard map \(\mathcal I_D:u_N\mapsto\psi_N^{\rm lock}\), the scalar two-center spectral operator and the quantities \((g_N^{\rm chiral},\Gamma_N,B_N,P_N)\) define an effective model for how these three protected modes form and couple to the visible sector.
They are coarse-grained phenomenological structures on top of the Spin\(^c\) generation theorem, not substitutes for it.

\begin{acknowledgments}
The author acknowledges the mathematical foundations of Riemann surface theory, Spin\(^c\) Dirac operators, index theory, and Standard Model anomaly cancellation used in this work.
\end{acknowledgments}

\begin{thebibliography}{99}

\bibitem{Hartshorne1977}
R.~Hartshorne,
\textit{Algebraic Geometry},
Graduate Texts in Mathematics Vol.~52,
Springer (1977).

\bibitem{GriffithsHarris1978}
P.~Griffiths and J.~Harris,
\textit{Principles of Algebraic Geometry},
Wiley (1978).

\bibitem{Forster1981}
O.~Forster,
\textit{Lectures on Riemann Surfaces},
Graduate Texts in Mathematics Vol.~81,
Springer (1981).

\bibitem{LawsonMichelsohn1989}
H.~B.~Lawson and M.-L.~Michelsohn,
\textit{Spin Geometry},
Princeton University Press (1989).

\bibitem{Nakahara2003}
M.~Nakahara,
\textit{Geometry, Topology and Physics},
2nd ed.,
Institute of Physics Publishing (2003).

\bibitem{Bertlmann1996}
R.~A.~Bertlmann,
\textit{Anomalies in Quantum Field Theory},
Oxford University Press (1996).

\bibitem{Bilal2008}
A.~Bilal,
``Lectures on Anomalies,''
arXiv:0802.0634.

\bibitem{BirrellDavies1982}
N.~D.~Birrell and P.~C.~W.~Davies,
\textit{Quantum Fields in Curved Space},
Cambridge University Press (1982).

\bibitem{Feshbach1958}
H.~Feshbach,
``Unified theory of nuclear reactions,''
Annals Phys. \textbf{5}, 357 (1958).

\bibitem{ReedSimon4}
M.~Reed and B.~Simon,
\textit{Methods of Modern Mathematical Physics IV: Analysis of Operators},
Academic Press (1978).

\end{thebibliography}

\end{document}
